Enrich the datasets with new columns.

### 2020-08-19 inst/analysis/enrich_dataset.Rmd
Keeping on decreasing the size of the dataset

---
title: "Enrich the datasets with new columns."
output:
  rmdformats::readthedown:
        code_folding: hide
        lightbox: true
        gallery: false
        df_print: paged
        toc_depth: 3
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  data_dirpath: "/var/lib/R/project-evalR/run/package-evals-traced-corpus.3/"
  data_filepath: "/var/lib/R/project-evalR/run/package-evals-traced-corpus.3/calls.fst"
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "html") })
---

@@

```{r load-data, echo=FALSE}
eval_calls <-
    read_fst(params$data_filepath) %>%
    filter(!caller_function %in% eval_base_functions) %>%
    as_tibble() %>%
    mutate(eval_call_package = map_chr(eval_call_srcref, extract_package_name)) %>% 
    resolve_sexp_name(expr_expression_type) %>%
    resolve_sexp_name(expr_resolved_type) %>%
    resolve_sexp_name(enclos_type) %>%
    resolve_sexp_name(envir_type)
```

```{r}
eval_calls <-  eval_calls %>% mutate(function_expr = if_else(expr_expression_type == "LANGSXP", map_chr(expr_expression, function_name), NA), function_expr_resolved = if_else(expr_resolved_type == "LANGSXP", map_chr(expr_resolved, function_name), NA))
```

```{r}
eval_calls <- eval_calls %>% mutate(parse_args = if_else(is.na(expr_parsed_expression), NA, map(expr_parsed_expression, extract_args_parse)))
```

```{r write_back}
write_fst(eval_calls, paste0(params$data_dirpath, "enriched_calls.fst"))
```

>>>>

---
title: "Enrich the datasets with new columns."
output:
  rmdformats::readthedown:
        lightbox: true
        gallery: false
        df_print: paged
        toc_depth: 3
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  data_dirpath: "/var/lib/R/project-evalR/run/package-evals-traced-corpus.3/"
  data_filepath: "/var/lib/R/project-evalR/run/package-evals-traced-corpus.3/calls.fst"
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "html") })
---

@@

```{r load-data, echo=FALSE}
eval_calls_raw <-
    read_fst(params$data_filepath) %>%
    as_tibble()

eval_calls <- eval_calls_raw %>% filter(!caller_function %in% eval_base_functions)
```

There are so many calls that are similar:
```{r}
eval_calls_base <- eval_calls_raw %>% filter(caller_function %in% eval_base_functions) 
```

Let's remove the duplicate ones:

```{r}
eval_calls_base <- eval_calls_base %>% select(-eval_call_id, -starts_with("caller_stack")) %>% distinct()

eval_calls <- eval_calls_base %>% select(-eval_call_id) %>% distinct()
```

```{r}
eval_calls_base <- eval_calls_base %>% 
    resolve_sexp_name(expr_expression_type) %>%
    resolve_sexp_name(expr_resolved_type) %>%
    resolve_sexp_name(enclos_type) %>%
    resolve_sexp_name(envir_type)

eval_calls <- eval_calls %>% 
    mutate(eval_call_package = extract_package_name(eval_call_srcref, file)) %>% 
    resolve_sexp_name(expr_expression_type) %>%
    resolve_sexp_name(expr_resolved_type) %>%
    resolve_sexp_name(enclos_type) %>%
    resolve_sexp_name(envir_type)
```

```{r}
# We are doing some work once again! Parsing what was deparsed previously...
eval_calls <-  eval_calls %>% mutate(function_expr = if_else(expr_expression_type == "LANGSXP", map_chr(expr_expression, function_name), NA), function_expr_resolved = if_else(expr_resolved_type == "LANGSXP", map_chr(expr_resolved, function_name), NA))
```

```{r}
eval_calls <- eval_calls %>% mutate(parse_args = if_else(is.na(expr_parsed_expression), NA, map_chr(expr_parsed_expression, extract_args_parse)))
```

```{r write_back}
write_fst(eval_calls, paste0(params$data_dirpath, "enriched_calls.fst"))

write_dst(eval_calls_base, paste0(params$data_dirpath, "base_calls.fst"))
```
